---
title: "p8015_hw5_yh3430"
author: "Yu He"
date: "11/11/2021"
output: github_document
---

Load library
```{r}
library(tidyverse)
library(rvest)
```

## Problem 1

Let's import and clean the homicides data gathered by The Washington Post.

```{r}
homicide_df =
  read_csv("homicide_data.csv", na = c("", "Unknown")) %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
  
```


Focus on the Baltimore, MD

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")
  
baltimore_summary =
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test =
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n)
)

baltimore_test %>% 
  broom::tidy()
```

Let's try to iterate for all cities - 'function' to 'map'
Function for sample cities.

```{r}
prop_test_function = function(city_df){
  
  city_summary =
  city_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

  city_test =
    prop.test(
    x = city_summary %>% pull(unsolved),
    n = city_summary %>% pull(n)
  )

  return(city_test)
 
}

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Let's work on all cities - 'map"

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_result = map(data, prop_test_function),
    tidy_result = map(test_result, broom::tidy)
  ) %>% 
  select(city_state, tidy_result) %>% 
  unnest(tidy_result) %>% 
  select(city_state, estimate, starts_with("conf"))

```

Makes a plot about estimate and CIs for all cities

```{r}
results_df %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

ideas about summarize within cities to obtain the total number of homicides and the number of unsolved homicides

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_result = map2(unsolved, n, prop.test),
    tidy_result = map(test_result, broom::tidy)
  ) %>% 
  select(city_state, tidy_result) %>% 
  unnest(tidy_result) %>% 
  select(city_state, estimate, starts_with("conf"))
```


## Problem 2

Step 1 - Using 'map' import data of participants. create a variable that contain the imported file (list - iteration)

```{r}

study_df = 
   tibble(
    files = list.files("./data")
  ) %>% 
  mutate(
    files = list.files("./data", pattern = ".csv", full.names = TRUE),
    study_result = map(set_names(files), read_csv)
  ) %>% 
  unnest()

```

Step 2 - data manipulation, add a variable indicate the study arm, tidy the data.

```{r}
study_data =
  study_df %>% 
  mutate(
    subject_id = str_sub(files, 8, 13)
  ) %>% 
  mutate(
    study_arm = str_sub(subject_id, 1, 3),
    study_arm = recode(study_arm, "con" = "control", "exp" = "experiment")
    ) %>% 
  relocate(study_arm, subject_id) %>% 
  select(-files) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value"
  )
  
```

Step 3 - making the spaghetti plot of subjects over time. 

The figure. 1 is the comparison between two study groups, which shows that the overall study results of experiment groups are significantly low than the study results of control groups. In addition, the overall trend of experiment groups remain roughly steady. And the overall trend of control group increases as the study week goes. 

```{r}
study_data %>% 
  ggplot(aes(x = week, y = value, group = subject_id, color = study_arm)) +
    geom_path() + 
    labs(
      title = "figure. 1 comparison between two study groups",
      caption = "Observations on each subject over time") + 
    viridis::scale_color_viridis(
      discrete = TRUE) 
```

```{r}
study_data %>% 
  ggplot(aes(x = week, y = value, group = study_arm, color = subject_id)) +
    geom_path() + 
    labs(
      title = "figure. 2 comparison of each study participants",
      caption = "Observations on each subject over time") + 
    viridis::scale_color_viridis(
      discrete = TRUE)
```



## Problem 3

load the dataset

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

start with a function

```{r}
fill_in_missing = function(missing_value) {
  
  if (is.numeric(missing_value)) {
    missing_value[is.na(missing_value)] <- mean(missing_value, na.rm = TRUE)
    }
  
  if (is.character(missing_value)) {
    missing_value[is.na(missing_value)] <- "Virginica"
  }
  
  return(missing_value)
  
}
```


Let's try the function

```{r}

fill_in_missing(pull(iris_with_missing, sepal_length))
```

Let's use the iteration - ' map'


```{r}
iris_without_missing = 
  map_dfr(iris_with_missing, fill_in_missing) %>% 
  unnest(species)

iris_without_missing
```










